### 2018-11-22 si.tex
Bunch of stuff including replace figures.

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Supplementary Material: Joint modelling of aggregated incidence data and point prevalence surveys for malaria mapping} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Tim C.D. Lucas*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha \textsuperscript{1}, Rosalind Howes \textsuperscript{1}, Katherine Battle \textsuperscript{1}, Andre Python \textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Dan Weiss\textsuperscript{1}
\\
\bigskip
\textbf{1} BDI, Oxford
\\
\bigskip

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Supplementary Material: Joint modelling of aggregated incidence data and point prevalence surveys for malaria mapping} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Tim C.D. Lucas*\textsuperscript{1}, Anita Nandi\textsuperscript{1}, Michele Nguyen\textsuperscript{1}, Susan Rumisha \textsuperscript{1}, Rosalind Howes \textsuperscript{1}, Katherine E. Battle \textsuperscript{1}, Andre Python \textsuperscript{1}, Ewan Cameron\textsuperscript{1}, Pete Gething\textsuperscript{1} and Daniel J. Weiss\textsuperscript{1}
\\
\bigskip
\textbf{1} BDI, Oxford
\\
\bigskip
